\begin{thebibliography}{99}
	\bibitem{santarpia2020aerosol}Santarpia, J., Rivera, D., Herrera, V., Morwitzer, M., Creager, H., Santarpia, G., Crown, K., Brett-Major, D., Schnaubelt, E., Broadhurst, M. \& Others Aerosol and surface contamination of SARS-CoV-2 observed in quarantine and isolation care. {\em Scientific Reports}. \textbf{10}, 1-8 (2020)
    \bibitem{wang2020accurate}Wang, C., Sarsenbayeva, Z., Chen, X., Dingler, T., Goncalves, J., Kostakos, V. \& Others Accurate measurement of handwash quality using sensor armbands: Instrument validation study. {\em JMIR MHealth And UHealth}. \textbf{8}, e17001 (2020)
    \bibitem{zhang2013human}Zhang, M. \& Sawchuk, A. Human daily activity recognition with sparse representation using wearable sensors. {\em IEEE Journal Of Biomedical And Health Informatics}. \textbf{17}, 553-560 (2013)
    \bibitem{sztyler2016body}Sztyler, T. \& Stuckenschmidt, H. On-body localization of wearable devices: An investigation of position-aware activity recognition. {\em 2016 IEEE International Conference On Pervasive Computing And Communications (PerCom)}. pp. 1-9 (2016)
    \bibitem{sztyler2017position}Sztyler, T., Stuckenschmidt, H. \& Petrich, W. Position-aware activity recognition with wearable devices. {\em Pervasive And Mobile Computing}. \textbf{38} pp. 281-295 (2017)
    \bibitem{bhat2018online}Bhat, G., Deb, R., Chaurasia, V., Shill, H. \& Ogras, U. Online human activity recognition using low-power wearable devices. {\em 2018 IEEE/ACM International Conference On Computer-Aided Design (ICCAD)}. pp. 1-8 (2018)
    \bibitem{koping2018general}Köping, L., Shirahama, K. \& Grzegorzek, M. A general framework for sensor-based human activity recognition. {\em Computers In Biology And Medicine}. \textbf{95} pp. 248-260 (2018)
    \bibitem{lattanzi2022exploring}Lattanzi, E., Donati, M. \& Freschi, V. Exploring Artificial Neural Networks Efficiency in Tiny Wearable Devices for Human Activity Recognition. {\em Sensors}. \textbf{22}, 2637 (2022)
    \bibitem{cheng2010active}Cheng, J., Amft, O. \& Lukowicz, P. Active capacitive sensing: Exploring a new wearable sensing modality for activity recognition. {\em International Conference On Pervasive Computing}. pp. 319-336 (2010)
    \bibitem{singh2017convolutional}Singh, D., Merdivan, E., Hanke, S., Kropf, J., Geist, M. \& Holzinger, A. Convolutional and recurrent neural networks for activity recognition in smart environment. {\em Towards Integrative Machine Learning And Knowledge Extraction}. pp. 194-205 (2017)
    \bibitem{hassan2018robust}Hassan, M., Uddin, M., Mohamed, A. \& Almogren, A. A robust human activity recognition system using smartphone sensors and deep learning. {\em Future Generation Computer Systems}. \textbf{81} pp. 307-313 (2018)
    \bibitem{hou2020study}Hou, C. A study on IMU-based human activity recognition using deep learning and traditional machine learning. {\em 2020 5th International Conference On Computer And Communication Systems (ICCCS)}. pp. 225-234 (2020)
    \bibitem{muller2021ten}Muller, H., Mayrhofer, M., Van Veen, E. \& Holzinger, A. The ten commandments of ethical medical AI. {\em Computer}. \textbf{54}, 119-123 (2021)
    \bibitem{zhong2020multi}Zhong, C., Reibman, A., Mina, H. \& Deering, A. Multi-view hand-hygiene recognition for food safety. {\em Journal Of Imaging}. \textbf{6}, 120 (2020)
    \bibitem{yue2021intelligent}Yue, Z., Wang, F. \& Liu, Z. An intelligent hand-washing monitoring platform based on gesture recognition technology. {\em 2021 China Automation Congress (CAC)}. pp. 940-944 (2021)
    \bibitem{galluzzi2015hand}Galluzzi, V., Herman, T. \& Polgreen, P. Hand hygiene duration and technique recognition using wrist-worn sensors. {\em Proceedings Of The 14th International Conference On Information Processing In Sensor Networks}. pp. 106-117 (2015)
    \bibitem{bal2017system}Bal, M. \& Abrishambaf, R. A system for monitoring hand hygiene compliance based-on Internet-of-Things. {\em 2017 IEEE International Conference On Industrial Technology (ICIT)}. pp. 1348-1353 (2017)
    \bibitem{li2018wristwash}Li, H., Chawla, S., Li, R., Jain, S., Abowd, G., Starner, T., Zhang, C. \& Plötz, T. Wristwash: towards automatic handwashing assessment using a wrist-worn device. {\em Proceedings Of The 2018 ACM International Symposium On Wearable Computers}. pp. 132-139 (2018)
    \bibitem{jain2018gender}Jain, A. \& Kanhangad, V. Gender classification in smartphones using gait information. {\em Expert Systems With Applications}. \textbf{93} pp. 257-266 (2018)
    \bibitem{van2019systematic}Van Hamme, T., Garofalo, G., Argones Rúa, E., Preuveneers, D. \& Joosen, W. A systematic comparison of age and gender prediction on imu sensor-based gait traces. {\em Sensors}. \textbf{19}, 2945 (2019)
    \bibitem{mondol2015harmony}Mondol, M. \& Stankovic, J. Harmony: A hand wash monitoring and reminder system using smart watches. {\em Proceedings Of The 12th EAI International Conference On Mobile And Ubiquitous Systems: Computing, Networking And Services On 12th EAI International Conference On Mobile And Ubiquitous Systems: Computing, Networking And Services}. pp. 11-20 (2015)
    \bibitem{mondol2020hawad}Mondol, M. \& Stankovic, J. HAWAD: Hand washing detection using wrist wearable inertial sensors. {\em 2020 16th International Conference On Distributed Computing In Sensor Systems (DCOSS)}. pp. 11-18 (2020)
    \bibitem{banerjee2020hand}Banerjee, A., Amperyani, V. \& Gupta, S. Hand hygiene compliance checking system with explainable feedback. {\em Proceedings Of The 6th ACM Workshop On Wearable Systems And Applications}. pp. 34-36 (2020)
    \bibitem{samyoun2021iwash}Samyoun, S., Shubha, S., Mondol, M. \& Stankovic, J. iWash: A smartwatch handwashing quality assessment and reminder system with real-time feedback in the context of infectious disease. {\em Smart Health}. \textbf{19} pp. 100171 (2021)
    \bibitem{fagert2022clean}Fagert, J., Bonde, A., Srinidhi, S., Hamilton, S., Zhang, P. \& Noh, H. Clean Vibes: Hand Washing Monitoring Using Structural Vibration Sensing. {\em ACM Transactions On Computing For Healthcare}. (2022)
    \bibitem{lattanzi2022unstructured}Lattanzi, E., Calisti, L. \& Freschi, V. Unstructured Handwashing Recognition using Smartwatch to Reduce Contact Transmission of Pathogens. {\em IEEE Access}. (2022)
\end{thebibliography}